Implementing Real-time Transport Services over an Ossified Network

### 2016-05-15 paper.tex
Expand discussion of real-time transport services

...discussion of APIs and transport services for real-time applications

- deadlines
- partial reliability
- application-level framing and ADUs
- sub-streams
- etc.

what a conceptual API for this would look like

>>>>

In the IETF, the Transport Services (TAPS) working group is chartered to 
(1) develop a taxonomy of \emph{transport services}, i.e., to identify the
features that comprise, and can be combined, to form complete transport
protocols; and (2) to develop an abstract API for applications to request
desirable services, allowing the system to select an appropriate transport
protocol based on application needs. It is hoped that this will loosen the
coupling between application and transport, so enabling deployment of new 
transport protocols.

...TAPS is valuable, because it gives us a vocabulary for discussing the
   components of transport protocols, that we can use to identify the needs
   of real-time applications

...the key feature of such applications is clearly timing. That is, since
   these applications convey real-time data, they all have some concept 
   of a \emph{deadline} by which that data must be presented, after which it 
   becomes useless. 
   the deadline might be short or long. Interactive applications, such as
   telephony, video conferencing, or telepresence, require low end-to-end
   latency, with the deadline for presenting data being tens, or perhaps
   low hundreds, of milliseconds after it was generated. Non-interactive
   applications, such as broadcast TV, may have deadlines in the order of
   seconds, or even tens of seconds for on-demand programming. 
   These deadlines are unusual for real-time systems, in that they are
   simultaneously flexible and strict: flexible in that the exact value
   of the deadline is typically not important, provided it is of the 
   right order-of-magnitude for the application, but strict in that 
   any particular deadline provides a hard cut-off, after which the
   data is useless.

...the presence of deadlines, in a network that offers only a best-effort
   packet deliver service, implies that the transport must provide only
   \emph{partial reliability}.
   the network must be assumed to have non-zero probability of losing any
   particular packet. If FEC is used to repair loss, this implies there is
   always some probability that a particular packet will be non-recoverable. 
   If retransmission is used to repair loss, this implies that there is
   always the potential of unbounded delay. 
   These probabilities can be estimated and bounded, but will be non-zero.
   Accordingly, to meet deadlines, the transport must offer a partial
   reliability service. 
   Many real-time applications run over TCP today, and TCP does not offer
   this service. This results in occasional play-out stalls, when the
   transport blocks the application. These are one of the primary causes
   of poor user experience in streaming applications, and this is directly
   caused by the lack of partial reliability. Missing one frame that has
   not been delivered by its deadline is much less disruptive than a stall
   in play-out.

...given deadlines and partial reliability, the next important transport
   service is \emph{dependency management}. There is no point sending
   data that cannot be used, because it depends on previous data that
   was lost. 
   complex trade-off, since you might want to send data that misses its 
   deadline, if it allows later data to be used.

...following from this, we have the concept of application-level framing
   to make the best use of data, irrespective of losses. This implies that
   the transport provides a \emph{message oriented} service that respects
   ADU boundaries.

...we note that many multimedia applications make use of multiple streams. 
   For example, audio and video are logically separate, etc.
   can be supported by opening multiple transport connections, but
   desirable to support a \emph{sub-stream} service to reduce overheads.

...finally, we note that \emph{congestion control} is important. 
   motivate: historically there has been a belief that real-time doesn't 
   do congestion control, needs an isochronous channel. 
   not practical for the Internet. 
   Also, experience has shown not necessary for many real-time applications.
   Yes, there are some that need constant bandwidth and cannot adapt, but
   many are adaptive. 
   Better user experience to adapt to fit the channel, rather than recover
   from loss after the channel discards packets that don't fit.

..what a conceptual API for this would look like?
